### 2024-06-24 sections/reviewer.tex
Update reviewer.tex

\begin{itemize}
\item{\small Associate Editor in {\itshape Revista de Gestión Pública} (ISSN 0719-1820), Universidad de Valparaíso, CHL, {\itshape since} 2016}
\item{\small Editor in {\itshape Tufte Working Papers} (ISSN 2735-6043), Training Data Lab, CHL, {\itshape since} 2020}
\item{\small Moderator in {\itshape SocArXiv}, University of Maryland, USA, {\itshape since} 2023}
\item{\small Experts Network for Transparency, Pan American Development Foundation, ECU, {\itshape since} 2022}
\item{\small Master in Management and Public Policy, Universidad de Santiago de Chile (USACH), CHL, {\itshape since} 2022}
\item{\small Reviewer in {\scshape WoS-SSCI}, {\scshape Scopus}, \& {\scshape WoS-ESCI} journals, {\itshape since} 2013}
\item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, {\itshape since} 2013}
\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, NLD, 2018, 2019, 2022-2023}
\item{\small Varieties of Democracy Project, University of Gothenburg, SWE, 2014, 2018-2020}
\item{\small Global Academic Reputation Survey, Clarivate Analytics, USA, 2020}
\item{\small Sectoral Commission for Research, Universidad de la República, URY, 2016, 2018}
\end{itemize}

>>>>

\begin{itemize}
\item{\small Moderator in {\itshape SocArXiv}, University of Maryland, USA, {\itshape since} 2023}
\item{\small Master in Economic History, Universidad de Santiago de Chile (USACH), CHL, {\itshape since} 2023}
\item{\small Experts Network for Transparency, Pan American Development Foundation, ECU, {\itshape since} 2022}
\item{\small Master in Management and Public Policy, Universidad de Santiago de Chile (USACH), CHL, {\itshape since} 2022}
\item{\small Editor in {\itshape Tufte Working Papers} (ISSN 2735-6043), Training Data Lab, CHL, {\itshape since} 2020}
\item{\small Associate Editor in {\itshape Revista de Gestión Pública} (ISSN 0719-1820), Universidad de Valparaíso, CHL, {\itshape since} 2016}
\item{\small Reviewer in {\scshape WoS-SSCI}, {\scshape Scopus}, \& {\scshape WoS-ESCI} journals, {\itshape since} 2013}
\item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, {\itshape since} 2013}
\item{\small Varieties of Democracy Project, University of Gothenburg, SWE, 2014, 2018-2020, 2024}
\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, NLD, 2018-2019, 2022-2023}
\item{\small Global Academic Reputation Survey, Clarivate Analytics, USA, 2020}
\item{\small Sectoral Commission for Research, Universidad de la República, URY, 2016, 2018}
\end{itemize}
